%%%%% Abstract %%%%%
\section*{Abstract} 
The robotic manipulator plays a crucial role in alleviating labor burdens across diverse fields. This project has conceived a 
specialized modular fishbone continuum manipulator platform with 5 DoF, uniquely designed for medical applications. The 
manipulation of a Focused Ultrasound (FUS) transducer facilitates the precise eradication of tumor tissues within the human body.
The project encompassed methodologies for structural modeling, kinematics derivation, and the formulation of actuation control strategies.

Through these methodologies, a viable design solution for the continuum manipulator has been devised.  Implementing eight motors 
to paired control eight cables of the manipulator has facilitated the achievement of a 5-degree-of-freedom (5 DoF) 
configuration within a spacious workspace of 300x300x300mm. The resulting manipulator boasts user-friendly operation, affordability, 
and remarkable precision. 

Despite a series of strengths,  the manipulator exhibits its distinct limitations, requiring rectification through the 
introduction of a closed-loop control system, structural strength optimization, and refinement of kinematic algorithms 
to further enhance its performance. Looking forward, the project should focus on the transition to practical manufacturing. 
At this juncture, simulation results and parameters can be validated by constructing an actual prototype of the manipulator, 
ensuring the reliability of the simulations.


\vfill


\textbf{\emph{Key Words: Continuum Robotic, Therapeutic Ultrasound, Robot Kinematics, Strain Analysis, Arduino}}
\vspace{0.8cm}
\pagenumbering{gobble}
\setcounter{page}{1}
\newpage